A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2022-01-12 paper/elsarticle/elsarticle-template.tex
paper

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings lags well behind that of wearable AR systems such as handhelds or head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the ability to project augmentations only within the projector's own static field of view. Here, dynamic projection systems---using steerable mirror heads to direct the projection across wider areas---have the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of preparing the augmentations, in particular as the number of target locations in the scene becomes larger than a small handful. Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions (cf.\ Figure~\ref{fig:proj}). Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

\begin{figure}[t]
    \centering
    \subfloat[\centering Our warped image (to be projected).]{\raisebox{10mm}{\includegraphics[width=5cm]{images/projim_warped_scaled.png}}}
    \qquad
    \subfloat[\centering Projection from side to scene plane (viewed directly downwards to scene plane).]{{\includegraphics[width=6cm]{images/proj_projim_waped_full_.pdf}}}
    \caption{Projection to a given target location in the scene plane, correcting for projective distortions in terms of a \textit{virtual} projector placed and utilized according to our approach. (a) Original image (cf.\ Figure~\ref{fig:proj}(a)) warped using our approach. (b) Projecting the warped image to the scene plane from the viewpoint of the projector (bottom left, frustum in black with up vector red; same as in Figure~\ref{fig:proj}(b)) directed to the target location has the effect of projecting the \textit{original} image from the viewpoint of a virtual projector (center, frustum in gray with up vector red). This renders the projection free of projective distortions, aligned with the axes of the virtual camera, and at the desired metric scale. Note that black pixels will in effect be ignored by the projector.}
    \label{fig:warp}
\end{figure}

Our contribution is to propose a wide-area spatial AR system for planar scenes that produces the effect of keystone correction analytically, free of any manual interaction. Notably, we do this in a manner placing the $X$- and $Y$-axes of the augmentation in accordance with the $X$- and $Y$-axes of a camera placed to face downwards towards the scene plane (cf.\ Figure~\ref{fig:eval}(a)). In what follows,  \textit{we shall refer to this camera as `downwards facing'} for brevity, in quotes since the pose of the camera is likely to deviate at least gently from facing downwards towards the scene plane directly (an effect for which we shall carry out a correction). Relying on the placement of the `downwards-facing' camera thus facilitates placement of augmentations, since setting the $X$- and $Y$-axes of augmentations with respect to the scene plane thus reduces to appropriately rotating the `downwards-facing' camera relative to the scene plane. We compute our corrective image warp for a given target location by warping the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but in accordance with the viewpoint of a \textit{virtual} projector (cf.\ Figure~\ref{fig:warp}). We place this virtual projector to (i) face directly downwards to the target location in the scene plane and (ii) rotate its axes to match those of the virtual camera. Moreover, our system enables specifying the dimensions of augmentations in metric terms, which we achieve by placing the virtual projector at the appropriate height above the scene plane. Finally, our system is set up for use with a projector equipped with a steerable mirror in a manner that does not call for explicitly modeling the action of the steerable mirror on the projector, thereby enabling wide-area applications exceeding the immediate field of view of the projector without needing to rely on multiple projectors.

@@

One way to compute such a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface \cite{Hartley2004}. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Additional sensors can be used to inform the computation of a homography; Raskar and Beardsley \cite{raskar2001self} use a tilt sensor to recover the projector's gravity vector relative to the projector, which they use to carry out a rotational correction in projecting to a wall. Still another way to compute a homography is as a function of a plane and a pair of pinhole cameras; the effect produced by the homography is one of projecting an image to the plane from the viewpoint of the one camera, and acquiring the projected image from the viewpoint of the other. Such a homography is said to be `induced' by a plane \cite{Hartley2004}. We exploit the fact that cameras and projectors alike can be modeled using a pinhole camera model \cite{bimber2019spatial}, proceed to recover the relative geometry relating the scene plane and projector, and compute a particular form of plane-induced homography to effect the intended corrective image warp, yet additionally taking into account both desired in-plane orientation and metric scale.

@@

A camera can be calibrated by (i) establishing 2D-3D correspondences between pixels in the camera's image plane and the corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output maximum likelihood estimates of the calibration matrix, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D scene points from among the 2D-3D correspondences \cite{Hartley2004,zhang2000flexible}. Calibration images containing a calibration surface such as a chessboard pattern of known dimensions and scale are acquired from varying viewpoints using the camera, to be used to establish the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is then used to obtain the maximum likelihood estimates~$(\hat{\omega}, \hat{\mathtt{K}}, \{(\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)\}), j \in \{ 1, \dots, n_\text{im} \}$ of the lens distortion model coefficients~$\omega$, calibration matrix~$\mathtt{K}$, and rigid body transformations~$(\mathtt{R}_j, \mathbf{t}_j), j \in \{ 1, \dots, n_\text{im} \}$. These are obtained using bundle adjustment by minimizing the cumulative reprojection error
\begin{equation}
\sum_{i=1}^{n_\text{pt}} \sum_{j=1}^{n_\text{im}} d_{\hat{\omega}}(\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'),
\label{re}
\end{equation}
where $\hat{\mathbf{x}}_{i,j}' \in \mathbb{R}^2$ gives the projection of the point~$\mathbf{X}_{i,j} \in \mathbb{R}^3$ to the image plane of the camera underlying the $j^{\text{th}}$~calibration image, subject to the maximum likelihood estimates $\hat{\mathtt{K}}, (\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)$. The function~$d_{\hat{\omega}}$, in turn, is a function that first (i) corrects $\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'$ for lens distortions in accordance with the maximum likelihood estimate of the lens distortion model coefficients~$\hat{\omega}$ \cite{duane1971close,weng1992camera}, and then (ii) computes a distance in pixels with respect to two resulting corrected positions. More generally, the projection~$\mathbf{x}' \in \mathbb{R}^2$ of a point~$\mathbf{X} \in \mathbb{R}^3$ to the image plane of a camera given calibration matrix~$\mathtt{K}$ and pose~$(\mathtt{R}, \mathbf{t})$ is given by
\begin{equation}
(\mathbf{x}'^\top, 1)^\top \sim \mathtt{K}(\mathtt{R}\mathbf{X} + \mathbf{t}) \in \mathbb{P}^2,
\end{equation}
where $\mathtt{R}\mathbf{X} + \mathbf{t} \in \mathbb{R}^3$ expresses $\mathbf{X}$ in the coordinate frame of the camera. Inverting the rigid body transformation~$(\mathtt{R}_j, \mathbf{t}_j)$ gives the pose~$(\mathtt{R}_j^{-1}, -\mathtt{R}_j^{-1}\mathbf{t}_j^{})$ of the $j^{\text{th}}$~camera relative to the 3D scene points of the calibration pattern, with $-\mathtt{R}_j^{-1}\mathbf{t}_j^{} \in \mathbb{R}^3$ the corresponding center of projection.

@@

\begin{figure}[t]
    \centering
    \subfloat[\centering Oblique view (annotated).]{{\includegraphics[height=5.25cm]{images/3_cam.pdf}}}
    \qquad
    \subfloat[\centering View directly downwards to scene~plane.]{{\includegraphics[height=5.25cm]{images/3_above3_cam.png}}}
    \caption{Obtaining the virtual camera. Our physical `downwards-facing' camera---placed to face downwards towards the scene plane, and in terms of whose rotation relative to the normal vector of the scene plane we wish to orient our augmentations---is almost certain to not face downwards towards the scene plane precisely. Accordingly, we rotate the recovered `downwards-facing' camera (frustum in black) about its center of projection such that its optical axis be made parallel with the scene plane's normal, with respect to the minimum arc-length rotation relating the two.} %It is then, for each respective target location, the $X$- and $Y$-axes of the resulting \textit{virtual} camera (gray) that we subsequently use to orient the virtual projector (cf.\ Figure~\ref{fig:virtualproj}) in terms of which the augmentation is to appear to be projected, which is itself placed to face downwards towards the scene plane precisely. The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera. This rotated camera is our virtual camera, and it is the orientation of the virtual camera that we subsequently use to orient our virtual projector.
    \label{fig:virtualcam}
\end{figure}

@@

\paragraph{Virtual camera and projector} The placement of the virtual projector---for a given a target location---determines from which pose the image to be projected is to \textit{appear} to have been projected, with the effect of (i) correcting for projective distortions, (ii) placing the axes of the augmentation in accordance with the axes of the `downwards-facing' camera, and (iii) setting the dimensions of the augmentation in line with the desired target dimensions.  We carry out this placement according to a small handful of steps. It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation, since we wish to intuitively be able to use the rotation of the camera relative to the scene plane to set those axes. It is, however, only if the virtual projector be placed to face downwards to the scene plane precisely that the projection will appear free of distortions; this is noteworthy, since a physical camera placed to face downwards is almost certain to not face precisely downwards to the scene plane. Accordingly, we rotate the recovered camera about its center of projection to align its optical axis\footnote{Strictly speaking, the optical axis is the back-projection of the principal point; in our usage, we understand it to refer to the ray through center of the image plane.} with the normal vector of the scene plane by applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}). To obtain the virtual projector, we then (i) intersect the scene plane with the optical axis of the projector and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector, and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired metric projected image dimensions; the height $h$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}

>>>>

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings lags well behind that of wearable AR systems such as handhelds or head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the ability to project augmentations only within the projector's own static field of view. Here, dynamic projection systems---using steerable mirror heads to direct the projection across wider areas---have the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of preparing the augmentations, in particular as the number of target locations in the scene becomes larger than a small handful.

Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions (cf.\ Figure~\ref{fig:proj}). More generally, na\"ively projecting an image to a planar surface causes not only projective distortions as a function of target location, but also variation in scale and orientation. Such effects can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

\begin{figure}[t]
    \centering
    \subfloat[\centering Our warped image (to be projected).]{\raisebox{10mm}{\includegraphics[width=5cm]{images/projim_warped_scaled.png}}}
    \qquad
    \subfloat[\centering Projection from side to scene plane (viewed directly downwards to scene plane).]{{\includegraphics[width=6cm]{images/proj_projim_waped_full_.pdf}}}
    \caption{Projection to a given target location in the scene plane, correcting for projective distortions in terms of a \textit{virtual} projector placed and utilized according to our approach. (a) Original image (cf.\ Figure~\ref{fig:proj}(a)) warped using our approach. (b) Projecting the warped image to the scene plane from the viewpoint of the projector (bottom left, frustum in black with up vector red; same as in Figure~\ref{fig:proj}(b)) directed to the target location has the effect of projecting the \textit{original} image from the viewpoint of a virtual projector (center, frustum in gray with up vector red). This renders the projection free of projective distortions, oriented in accordance with the axes of the `downwards-facing' camera, and at the desired metric scale. Note that black pixels will in effect be ignored by the projector.}
    \label{fig:warp}
\end{figure}

Our contribution is to propose a spatial AR system for planar scenes that produces the effect of manual keystone correction analytically in a manner for use with a projector equipped with a steerable mirror, thereby enabling wide-area applications exceeding the immediate field of view of the projector without needing to rely on multiple projectors. Besides correcting for projective distortions, our system enables placement of augmentations at a desired metric scale. Notably, the system moreover enables setting the $X$- and $Y$-axes of the augmentation in accordance with the $X$- and $Y$-axes of a camera placed to face downwards towards the scene plane (cf.\ Figure~\ref{fig:eval}(a)), which in our case is a factory floor (but could well be generalized to other planar surfaces). We refer to this camera as `downwards facing' for brevity, in quotes since the camera likely to deviate at least gently from facing downwards towards the scene plane directly.\footnote{More precisely, we understand a camera to face downwards towards the scene plane \textit{directly} if the camera's optical axis is parallel with the scene plane's normal vector, and correct for possible deviation.} Relying on the placement of the `downwards-facing' camera to orient augmentations substantially facilitates placement relative to manual keystone correction, since setting the $X$- and $Y$-axes of augmentations thus reduces to appropriately rotating the `downwards-facing' camera relative to the scene plane.

We compute our corrective image warp for a given target location by warping the image to be projected using a plane-induced homography computed to produce the effect of projecting the image not from the actual projector viewpoint, but from the viewpoint of a \textit{virtual} projector (cf.\ Figure~\ref{fig:warp}). We place this virtual projector to (i) face directly downwards to the target location in the scene plane and (ii) rotate its axes in accordance with those of the `downwards-facing' camera. Finally, we (iii) place the virtual projector at the appropriate height above the scene plane to produce the augmentation with the desired metric dimensions in the scene plane.

@@

One way to compute such a homography is by identifying at least four correspondences between pixel positions in two images of a planar surface \cite{Hartley2004}. The keystone correction approach of Sukthankar \textit{et al.} \cite{sukthankar2001smarter} reduces to using a segmentation approach to identify the four corners of projection screen in an image acquired by a camera, and computing a homography that maps the resulting four corners of the projection screen to the four corners of the projector's image plane. Additional sensors can be used to inform the computation of a homography; Raskar and Beardsley \cite{raskar2001self} use a tilt sensor to recover the projector's gravity vector relative to the projector, which they use to carry out a rotational correction in projecting to a wall.

Still another way to compute a homography is as a function of a plane and a pair of pinhole cameras; the effect produced by the homography is one of projecting an image to the plane from the viewpoint of the one camera, and acquiring the projected image from the viewpoint of the other. Such a homography is said to be `induced' by a plane \cite{Hartley2004}. We exploit the fact that cameras and projectors alike can be modeled using a pinhole camera model \cite{bimber2019spatial}, proceed to recover the relative geometry relating the scene plane and projector, and compute a particular form of plane-induced homography to effect the intended corrective image warp, additionally taking into account both desired in-plane orientation and metric scale.

@@

A camera can be calibrated by (i) establishing 2D-3D correspondences between pixels in the camera's image plane and the corresponding points in the scene, and on (ii) using those correspondences as input to an optimization procedure that relies on bundle adjustment \cite{triggs1999bundle} to output maximum likelihood estimates of the calibration matrix, the associated lens distortion model coefficients, and, for each calibration image, the pose (i.e., position and orientation) of the camera relative to the 3D scene points from among the 2D-3D correspondences \cite{Hartley2004,zhang2000flexible}.

Calibration images containing a calibration surface such as a chessboard pattern of known dimensions and scale are acquired from varying viewpoints using the camera, to be used to establish the 2D-3D correspondences~$\{\mathbf{x}_{i,j} \leftrightarrow \mathbf{X}_{i,j}\}$, $i \in \{ 1, \dots, n_\text{pt} \}, j \in \{ 1, \dots, n_\text{im} \}$, where $n_\text{pt}$ gives the number of correspondences obtained from one calibration image of the pattern, $n_\text{im}$ the number of such images, and $\mathbf{X}_{i,j} = \mathbf{X}_{i,j'}$, for $j, j' \in \{ 1, \dots, n_\text{im} \}$. Bundle adjustment is then used to obtain the maximum likelihood estimates~$(\hat{\omega}, \hat{\mathtt{K}}, \{(\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)\}), j \in \{ 1, \dots, n_\text{im} \}$ of the lens distortion model coefficients~$\omega$, calibration matrix~$\mathtt{K}$, and rigid body transformations~$(\mathtt{R}_j, \mathbf{t}_j), j \in \{ 1, \dots, n_\text{im} \}$. These are obtained using bundle adjustment by minimizing the cumulative reprojection error
\begin{equation}
\sum_{i=1}^{n_\text{pt}} \sum_{j=1}^{n_\text{im}} d_{\hat{\omega}}(\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'),
\label{re}
\end{equation}
where $\hat{\mathbf{x}}_{i,j}' \in \mathbb{R}^2$ gives the projection of the point~$\mathbf{X}_{i,j} \in \mathbb{R}^3$ to the image plane of the camera underlying the $j^{\text{th}}$~calibration image, subject to the maximum likelihood estimates $\hat{\mathtt{K}}, (\hat{\mathtt{R}}_j, \hat{\mathbf{t}}_j)$. The function~$d_{\hat{\omega}}$, in turn, is a function that first (i) corrects $\mathbf{x}_{i,j}, \hat{\mathbf{x}}_{i,j}'$ for lens distortions in accordance with the maximum likelihood estimate of the lens distortion model coefficients~$\hat{\omega}$ \cite{duane1971close,weng1992camera}, and then (ii) computes a distance in pixels with respect to two resulting corrected positions. More generally, the projection~$\mathbf{x}' \in \mathbb{R}^2$ of a point~$\mathbf{X} \in \mathbb{R}^3$ to the image plane of a camera given calibration matrix~$\mathtt{K}$ and pose~$(\mathtt{R}, \mathbf{t})$ is given by
\begin{equation}
(\mathbf{x}'^\top, 1)^\top \sim \mathtt{K}(\mathtt{R}\mathbf{X} + \mathbf{t}) \in \mathbb{P}^2,
\end{equation}
where $\mathtt{R}\mathbf{X} + \mathbf{t} \in \mathbb{R}^3$ expresses $\mathbf{X}$ in the coordinate frame of the camera. Inverting the rigid body transformation~$(\mathtt{R}_j, \mathbf{t}_j)$ gives the pose~$(\mathtt{R}_j^{-1}, -\mathtt{R}_j^{-1}\mathbf{t}_j^{})$ of the $j^{\text{th}}$~camera relative to the 3D scene points of the calibration pattern, with $-\mathtt{R}_j^{-1}\mathbf{t}_j^{} \in \mathbb{R}^3$ the corresponding center of projection.

@@

\begin{figure}[t]
    \centering
    \subfloat[\centering Oblique view (annotated).]{{\includegraphics[height=5.25cm]{images/3_cam.pdf}}}
    \qquad
    \subfloat[\centering View directly downwards to scene~plane.]{{\includegraphics[height=5.25cm]{images/3_above3_cam.png}}}
    \caption{Obtaining the virtual camera. Our physical `downwards-facing' camera---placed to face downwards towards the scene plane, and in terms of whose rotation relative to the normal vector of the scene plane we wish to orient our augmentations---is almost certain to not face downwards towards the scene plane directly. Accordingly, we rotate the recovered `downwards-facing' camera (frustum in black) about its center of projection such that its optical axis be made parallel with the scene plane's normal, with respect to the minimum arc-length rotation relating the two. It is the $X$- and $Y$-axes of the virtual camera that we then use to set the $X$- and $Y$-axes of the virtual projector.} %It is then, for each respective target location, the $X$- and $Y$-axes of the resulting \textit{virtual} camera (gray) that we subsequently use to orient the virtual projector (cf.\ Figure~\ref{fig:virtualproj}) in terms of which the augmentation is to appear to be projected, which is itself placed to face downwards towards the scene plane precisely. The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera. This rotated camera is our virtual camera, and it is the orientation of the virtual camera that we subsequently use to orient our virtual projector.
    \label{fig:virtualcam}
\end{figure}

@@

\paragraph{Virtual camera and projector} The placement of the virtual projector---for a given a target location---determines from which pose the image to be projected is to \textit{appear} to have been projected, with the effect of (i) correcting for projective distortions, (ii) placing the axes of the augmentation in accordance with the axes of the `downwards-facing' camera, and (iii) setting the dimensions of the augmentation in line with the desired target dimensions.  We carry out this placement according to a small handful of steps.

It is in accordance with the $X$- and $Y$-axes of the `downwards-facing' camera that we wish to place the $X$- and $Y$-axes of the augmentation, since we wish to intuitively be able to use the rotation of the camera relative to the scene plane to set those axes. It is, however, only if the virtual projector is placed to face downwards to the scene plane directly that the projection will appear free of distortions; this is noteworthy, since a physical camera placed to face downwards is almost certain to not face directly downwards to the scene plane. Accordingly, we rotate the recovered camera about its center of projection to align its optical axis with the normal vector of the scene plane by computing and applying the minimum arc-length rotation that relates the two, giving a \textit{virtual} camera facing directly downwards to the scene plane (cf.\ Figure~\ref{fig:virtualcam}).

To obtain the virtual projector, we (i) intersect the scene plane with the optical axis of the projector and rotate the projector's placement about that point of intersection, aligning the optical axis with the scene plane's normal vector, and (ii) align the $X$- and $Y$-axes with those of the virtual camera. Finally, we (iii) translate along the scene plane's normal, in order to satisfy the desired metric projected image dimensions; the height $h$ [m] above the ground plane at which the virtual projector is to be placed if the image---with original image width of $w_\text{im}$ [px]---is to be projected to the scene plane with a metric width of $w$ [m] is given by
\begin{equation}
h = w \times f_\text{proj} / w_\text{im},
\end{equation}
where $f_\text{proj}$ [px] is the focal length of the projector. These three steps are illustrated in Figure~\ref{fig:virtualproj}. The resulting virtual projector is thus rendered fronto-parallel with the scene plane---enabling projection to the scene plane absent of projective distortions---and projects to the scene plane in the desired scale and with the the $X$- and $Y$-axes of the augmentation set in accordance with those of the `downwards-facing' camera. %\footnote{A physical camera placed to face downwards is almost certain to not face downwards precisely; in contrast, we align the virtual camera's optical axis exactly with the scene plane's normal vector, rendering it genuinely fronto-parallel with respect to the scene plane.}
